---
title: "Attrition paper"
author: "Sophie Richter"
date: "11 October 2019"
output: html_document
---
This is the code for our paper:  
Richter, S., Stevenson, S., Newman, T., Wilson, L., Maas, A.I.R., Nieboer, D., Lingsma, H., Steyerberg, E., Newcombe, V., 2020. Study Design Features Associated with Patient Attrition in Studies of Traumatic Brain Injury — A Systematic Review 1–11. https://doi.org/10.1089/neu.2020.7000

# Data preparation 

```{r libraries, results='hide', message=FALSE, warning=FALSE}
#loading required libraries
library(magrittr)
library(naniar)
library(MASS)
library(dplyr)
library(forcats)
library(knitr)
library(kableExtra)
library(tidyr)
```

Load data
```{r}
#data collected for original review on the handling of missing data
handling.df      <- read.csv("mt.df_20180726.csv") 
#exclude study number 198 due to heterogeneous methodology
handling.df <- subset(handling.df, ID != 198)
#exclude studies that did not clearly report whether or not outcome data was missing
handling.df <- subset(handling.df, Report != "apparently complete data")

#additional data collected for this paper on study design features
design.df <- read.csv("Raw_slim_attrition_20190611.csv") #multiple design features
hdi.df <- read.csv("phready.df.csv") #feature: human development index
engage.df <- read.csv("BaseEffort_20190611.csv")# feature: Non-clinical engagement
gose.df <- read.csv("GOS_20190718.csv")#feature: method of GOSE collection

#combine data into a master dataframe
df <- merge(handling.df, design.df, 
            by = c("ID", "Author", "Year", "Reviewer"))
df <- merge(df, hdi.df, by = "ID", all.x = TRUE, all.y = FALSE)
df <- merge(df, engage.df, by = "ID")
df <- merge(df, gose.df, by = c("ID", "GOS.assessment"))
```

Summarizing Age for each study
```{r}
#making sure all NA are coded as such
df$Age_mean <- ifelse(df$Age_mean %in% c("", " ", "not reported", "Not reported"), NA, as.numeric(as.character(df$Age_mean)))

df$Age_median <- ifelse(df$Age_median %in% c("", " ", "not reported", "Not reported"), NA, as.numeric(as.character(df$Age_median)))

#Making a function to convert factor variables to numeric
fton <- function(factor_variable) {
  numeric_variable <- as.numeric(as.character(factor_variable))
  return(numeric_variable)
}

#Creating a variable Age that contains the mean age if available otherwise median age
  df$Age <- df %$% 
  ifelse(is.na(Age_mean), fton(Age_median), fton(Age_mean)) %>%
  round(0)
```

Select relevant columns i.e. those that refer to study design features rather than the way in which authors handled missing data statistically
```{r}
#select only relevant columns and give them more succinct names
df <- df %>% 
  select(ID, # study ID
         Author, # study author
         Year, # Year of publication
         Report,  # whether authors clearly reported if outcome data was missing
         N, # Number of patients enrolled initially
         Remaining, # Patients remaining at each follow up timepoint
         IntObs, # whether the study is interventional or observational
         RetroPro, # whether data was collected prospectively or retrospectively
         PrimSec, # whether GOSE was primary or secondary outcome
         Range, #whether follow up was at discrete timepoints or over a range of time
         Tpoints, #Total number of follow up timepoints in this study
         Timepoint = Timepoints, #is this the 1st, 2nd, 3rd, 4th or 5th follow up of this study
         Time, # time since injury
         Severity, #TBI injury severity
         Center, # single vs multicentre design
         Setting = Patients.were.identified.because.they.attended.were.admitted.to, #recruitment setting
         Military = Military.Population, # military or civilian cohort
         Male = Percent_Male, #sex
         Age, # age
         Engage =Baseline.or.Follow.up.effort, #level of non-clinical engagement required
         GOS1 = GOS1, # how GOS was collected (gross categorisation)
         GOS2 = GOS.assessment, # how GOS was collected (fine categorisation)
         Proxy = Was.proxy.assessment.accepted., # whether a proxy report of GOS was accepted
         HDI)
```

At the moment the data is in the long format i.e. there are several rows for each study. Each row refers to the nth follow-up timepoint for that study. For the purposes of this review, we are only interested in the the maximum number of patients lost by the end study. So we will only select the row referring to the final timepoint for each study and calculate the maximum number of patients lost by that point.
```{r}
#Recode Timepoint into a number (currently it's in the format "T1c", "T2c", "T3c" etc)
df$Timepoint <- gsub("T", "", df$Timepoint)
df$Timepoint <- gsub("c", "", df$Timepoint)
df$Timepoint <- as.numeric(df$Timepoint)

#Calculate the maximum number of patients lost in that study
df <-                           
  df %>%
  group_by(ID) %>% 
  summarise(MaxLost = max(I(N - Remaining), na.rm = TRUE)) %>% 
  merge(df) 

df$MaxLost <- ifelse(df$MaxLost == "-Inf", NA, as.numeric(df$MaxLost))

df$MinRemain <- df$N - df$MaxLost
df$MinRemain <- ifelse(df$MinRemain == "-Inf", NA, as.numeric(df$MinRemain))

#keep only one row per study, the one final timepoint
df <-  df %>% filter(Timepoint == Tpoints)
```


```{r}
str(df)
```
For each design feature, we need to tidy up the levels

```{r}
#Factorise ID
df$ID <- as.factor(df$ID)

#Percent_Male needs to be numeric
df$Male <- as.numeric(df$Male)


#RetroPro
df$RetroPro <-
  fct_collapse(df$RetroPro,
             Prospective = "Prospective",
             Retrospective = c("Both", "Retrospective AND prospective", "Retrospective"))
summary(df$RetroPro)%>% as.data.frame()


#Range
df$Range <- 
  fct_collapse(df$Range,
             no = c("", "no"),
             yes = "yes")
summary(df$Range)%>% as.data.frame()


#Severity
df <- df %>% replace_with_na(replace = list(Severity = "not reported"))
df$Severity <- factor(df$Severity) #removes redundant level
df$Severity <-
  fct_collapse(df$Severity,
             Moderate_to_severe = "moderate and severe",
             Mixed = c("all", "Mild and severe"),
             Mild = "mild only",
             Severe = "severe only")
summary(df$Severity)%>% as.data.frame()


#Center
df<- df %>% replace_with_na(replace = list(Center = ""))
df$Center <- factor(df$Center)
summary(df$Center)


#Setting
df<- df %>% replace_with_na(replace = list(Setting = c("", 
                                                       "Unclear", 
                                                       "Other", 
                                                       "Registry")))
df$Setting <- factor(df$Setting)
df$Setting <- 
  fct_collapse(df$Setting,
             Hyperacute = c("ED", "Pre-hospital"),
             Acute = c("ED, Ward or ICU", "ICU", "Ward or ICU", "ED or ICU"),
             Subacute = c("outpatient clinic", "Inpatient Rehab"))
summary(df$Setting) %>% as.data.frame()


#Engage
df$Engage <- factor(df$Engage, 
                       levels = c("NEITHER", "Baseline", "Follow-up","Both"), 
                       labels = c("none", "Baseline only", "Follow-up only", "Baseline and follow-up"))
summary(df$Engage) %>% as.data.frame()


#GOSE_how
df$GOS_how <- ifelse(df$GOS1 == "In person", "Exclusively in person", 
                     ifelse(df$GOS1 %in% c("In person or medical records", 
                                             "Mail or in person", 
                                             "Phone or in person", 
                                             "Phone or Mail or in person"), "Partially in person",
                            ifelse(df$GOS2 == "Not reported", NA, "Not in person")))
df$GOS_how <- factor(df$GOS_how, 
                       levels = c("Exclusively in person", "Partially in person", "Not in person"),
                       labels = c("Exclusively in person", "Partially in person", "Not in person"))
summary(df$GOS_how) %>% as.data.frame()
df <- df %>% select(-GOS1, -GOS2)


#Proxy
df<- df %>% replace_with_na(replace = list(Proxy = c("", 
                                                     "not reported", 
                                                     "Not reported",
                                                     "Not Reported",  
                                                     "Unclear")))
df$Proxy <- factor(df$Proxy)
summary(df$Proxy)


#Military
df$Military <- as.factor(df$Military)
df$Military <- droplevels(df$Military)
summary(df$Military)
```

# Make Table one
```{r}
library(tableone)
t1 <- df
t1$Perc <- (df$MaxLost/df$N) *100
t1 <- t1 %>% select(Perc, 
                    N, 
                    Time, 
                    Tpoints, 
                    Male,
                    Age,
                    Severity,
                    Military,
                    Center,
                    HDI,
                    Setting,
                    Engage,
                    PrimSec,
                    RetroPro,
                    Range, 
                    GOS_how,
                    Proxy, 
                    IntObs)

#Renaming the variables to something that looks good in the table 
names(t1) <- c("Percentage attrition by end of study",
            "Number of patients initially enrolled",
            "Study duration (months)",
            "Number of follow-up timepoints",
            "Male sex",
            "Age",
            "Injury severity based on GCS",
            "Military population",
            "Single-center (versus multi-center)",
            "Human development index of recruiting country",
            "Recruitment setting",
            "Non-routine clinical engagement",
            "GOS/GOSE as secondary (versus primary) outcome",
            "Prospective (versus retrospective) collection of outcome data",
            "Follow up at non-discrete timepoints",
            "Method for collecting GOS/GOSE outcome",
            "Proxy report of outcome was accepted",
            "Observational (versus interventional) design")
myvars <-  names(t1)[-length(names(t1))]

tab <- CreateTableOne(data = t1, vars = myvars, 
                      strata = "Observational (versus interventional) design")
#Storing the output as t1
t1 <- print(tab, 
      nonnormal = myvars, 
      test = F, 
      varlabels = T, 
      noSpaces = F, 
      printToggle = T,
      missing = T,
      contDigits = 2, 
      minMax = F,
      catDigits = 0,
      quote = F,
      explain = F, 
      dropEqual = T)

#making a pretty html version
t1 <- t1 %>% as.data.frame()
rownames(t1) <- gsub("\\.", " ", rownames(t1))
rownames(t1) <- gsub("X", " ", rownames(t1))
t1$Missing <- as.numeric(as.character(t1$Missing)) %>% round(0) %>% replace_na("")
colnames(t1) <- c( "Median [IQR] or Frequency (%)",  "Median [IQR] or Frequency (%)", "Percent of 148 studies")
t1 %>%
  kable(escape = FALSE) %>%
  kable_styling(bootstrap_options = c("condensed", "striped"), full_width = F) %>%
  add_indent(c( 9:12, 17:19, 21:24, 29:31)) %>%
  add_header_above(c("Design factor" = 1,"Interventional studies" = 1 ,"Observational studies" = 1,  "Design factor not reported" = 1))
```


# Multiple imputation of missing data
```{r}
set.seed(123) #ensure reproducible results
library(mice)
```

```{r}
#Remove excessive variables especially ID
df <- df %>% select(-ID,
                    -N,
                    -Year,
                    -Author,
                    -Report,
                    -Remaining)

#rescale time to 6 months intervals to avoid tiny numbers for the effect size per time unit
df$Time <- df$Time/6


```


```{r}
#Examine the pattern of missing data
md.pattern(df)
```


```{r}
#view fluxplot
fluxplot(df)
```


```{r}
#Making 1 imputed data set just to set up the methods
imp <- mice(df, m=1, print = F) 
#Show method of imputation used for each variable
imp$meth

```


```{r}
#Change imputation method for continuous variables
meth <- imp$meth
meth[c("Age", "Male", "MaxLost", "MinRemain")] <- "midastouch"
meth
```

```{r}
#Run the imputation again
imp <- mice(df, m= 20, meth = meth, print = F)
```


```{r}
imp #shows how data was imputed i.e. method and which variables contributed (I used all variables)
```



```{r}
#Check for convergence of imputations
plot(imp)
```


```{r}
#Check for plausibility on stripplots
stripplot(imp)
```


```{r}
#check for plausibility on density plots
densityplot(imp)
```
# Modelling the data

Visualise the outcome variable
```{r, include=TRUE}
hist(df$MaxLost, 100) #Absolute number of patients lost, disregarding study size
hist(log(df$MaxLost/df$MinRemain), 10) #logit of patients lost to follow up, i.e. considers study size
```
Run the model
```{r, include=TRUE}
#I am NOT using Proxy (75% missing and likely MNAR) and Military (too few studies are military) in the model
imputed_model <- with(imp, 
                      glm(cbind(MaxLost, MinRemain) ~ 
                Tpoints + 
                  Time + 
                  IntObs + 
                  RetroPro + 
                  PrimSec + 
                  Range + 
                  Severity + 
                  Center + 
                  Setting + 
                  Male + 
                  Age + 
                  Engage + 
                  GOS_how + 
                  HDI,
             family = binomial))
```

Create a results table for model coefficients
```{r, include=TRUE}
# log odds scale
sum <- summary(pool(imputed_model), conf.int = TRUE, exponentiate = TRUE)
sum[,-1] <- round(sum[,-1], 2)
sum
sum$sig <- ifelse(sum$`2.5 %` < 1 & sum$`97.5 %` <1, "*", 
                  ifelse(sum$`2.5 %` > 1 & sum$`97.5 %` > 1, "*", ""))

#merge columns for confidence interval
sum$CI <- paste(sum$`2.5 %`, "-", sum$`97.5 %`)
sum
#reorder and rename columns
sum <- sum %>% 
  select("Design factor" = term,
                      "Odds ratio" = estimate,
                      "95% Confidence Interval" = CI,
         "P-value" = p.value,
                      "Significant" = sig) 

sum <- sum[-1,] # remove intercepts
#save a copy for later
sum_imp <- sum


#reorder columns
myorder <-  c("Tpoints", "Time", "IntObsobservational", 
              "RetroProRetrospective", "PrimSecSecondary",  "Rangeyes", 
              "CenterSingle", "Male", "Age",  
              "HDI" ,"SeverityMild", "SeverityModerate_to_severe", 
              "SeveritySevere", "SettingAcute", "SettingSubacute",                                               "EngageBaseline only", "EngageFollow-up only", "EngageBaseline and follow-up",
              "GOS_howPartially in person",   "GOS_howNot in person")         
sum <- sum %>%
  mutate(`Design factor` =  factor(`Design factor`, levels = myorder)) %>%
  arrange(`Design factor`)

#Editing column Design factor
sum$`Design factor` <- gsub("Tpoints", "Total no. of follow-up timepoints",sum$`Design factor`)
sum$`Design factor` <- gsub("Time", "Study duration (per 6-months interval)",sum$`Design factor`)
sum$`Design factor` <- gsub("IntObsobservational", "Observational study (vs interventional)",sum$`Design factor`)
sum$`Design factor` <- gsub("RetroProProspective", "Prospective study (vs retrospective)",sum$`Design factor`)
sum$`Design factor` <- gsub("PrimSecSecondary", "GOS as secondary outcome (vs primary)",sum$`Design factor`)
sum$`Design factor` <- gsub("Rangeyes", "Use of follow-up time window (vs discrete timepoints)",sum$`Design factor`)
sum$`Design factor` <- gsub("Severity", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Setting", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Male", "Percentage of male patients",sum$`Design factor`)
sum$`Design factor` <- gsub("Age", "Mean age of study population",sum$`Design factor`)
sum$`Design factor` <- gsub("Engage", "",sum$`Design factor`)
sum$`Design factor` <- gsub("GOS_how", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Severe", "Severe only",sum$`Design factor`)
sum$`Design factor` <- gsub("CenterSingle", "Single-center study (vs multi-center)",sum$`Design factor`)
sum$`Design factor` <- gsub("HDI", "Human development index of recruiting country",sum$`Design factor`)
sum$`Design factor` <- gsub("_", " ",sum$`Design factor`)


#making a pretty html version
sum %>%
  kable(escape = FALSE, row.names= FALSE) %>%
  kable_styling(bootstrap_options = c("condensed", "striped"), full_width = F) %>%
  pack_rows("Recruitment setting (compared to the hyperacute setting)", 14, 15) %>%
  pack_rows("Level of non-routine engagement (compared to no such engagement)", 16, 18)%>%
  pack_rows("Method of GOS collection (compared to collection exclusively in person)", 19, 20) %>%
  pack_rows("Injury severity (compared to using patients of mixed severity)", 11,13 )

sum_imp
```


# Visualise predictions using the first of 20 imputed datasets

```{r}
#fit the model on just the first of 20 imputed dataset, so that it can be plotted
imp1 <- mice::complete(imp,1)
fit.imp1 <- with(imp1, glm(cbind(MaxLost, MinRemain) ~ 
                Tpoints + 
                  Time + 
                  IntObs + 
                  RetroPro + 
                  PrimSec + 
                  Range + 
                  Severity + 
                  Center + 
                  Setting + 
                  Male + 
                  Age + 
                  Engage + 
                  GOS_how + 
                  HDI,
             family = binomial))

```


```{r}
#load packages required for plotting
library("snakecase")
library("ggeffects")
library(ggplot2)
```

```{r}
#Plot Attrition based on recruitment setting and injury severity
mydf <- ggpredict(fit.imp1, c("Tpoints", "Severity", "Setting"))

p1 <- ggplot(mydf, aes(x, exp(predicted), group = group)) + 
  geom_point(aes(shape = group, colour = group), size = 4)+
  geom_line(aes(colour = group)) +
  geom_ribbon(aes(ymin = exp(conf.low), ymax = exp(conf.high)), alpha = .05)+
  facet_grid(.~facet) +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))+
  labs(title= "Attrition based on recruitment setting and injury severity ", 
       x="Number of follow-up timepoints", 
       y ="Odds of attrition by end of study")+
  #to combine legend for colour and shape into one
  scale_colour_manual(name = "Injury severity",
                      labels = c("mixed", "mild only", "moderate & severe", "severe only"),
                      values = c("red", "green", "orange", "blue")) +
  scale_shape_manual(name = "Injury severity",
                      labels = c("mixed", "mild only", "moderate & severe", "severe only"),
                     values = c(1, 2, 0, 3))


```

```{r}
#Plot Attrition based on recruiting centers and method of GOS collection
mydf <- ggpredict(fit.imp1, c("Tpoints", "Center", "GOS_how"))

p2 <- ggplot(mydf, aes(x, exp(predicted), group = group)) + 
  geom_point(aes(shape = group, colour = group), size = 4)+
  geom_line(aes(colour = group)) +
  geom_ribbon(aes(ymin = exp(conf.low), ymax = exp(conf.high)), alpha = .05)+
  facet_grid(.~facet) +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))+
  labs(title= "Attrition based on recruiting centers and method of GOS collection", 
       x="Number of follow-up timepoints", 
       y ="Odds of attrition by end of study")+
  #to combine legend for colour and shape into one
  scale_colour_manual(name = "Single vs Multi-Center",
                      labels = c("Multi-Center", "Single-Center"),
                      values = c("blue", "red")) +
  scale_shape_manual(name = "Single vs Multi-Center",
                      labels = c("Multi-Center", "Single-Center"),
                     values = c(0, 1))


```



```{r}
#plot Attrition based on time since injury and nnumber of follow-up timepoints
mydf <- ggpredict(fit.imp1, c("Time", "Tpoints"))

p3 <- ggplot(mydf, aes(x*6, exp(predicted), group = group )) + 
  geom_point(aes(shape = group, colour = group), size = 4)+
  geom_line(aes(colour = group)) +
  geom_ribbon(aes(ymin = exp(conf.low), ymax = exp(conf.high)), alpha = .05)+
  theme_bw(base_size = 28) +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5))+
  labs(title= "Attrition based on time since injury and \nnumber of follow-up timepoints", 
       x="Time since injury (months)", 
       y ="Odds of attrition by end of study" )+
  #to combine legend for colour and shape into one
 scale_colour_manual(name = "Total no. of \nfollow-up \ntimepoints",
                      labels = c("5", "4", "3", "2", "1"),
                      values = c("orange", "red", "purple", "blue", "green"),
                      limits = c("5", "4", "3", "2", "1")) +
  scale_shape_manual(name = "Total no. of \nfollow-up \ntimepoints",
                     labels = c("5", "4", "3", "2", "1"),
                     values = c(0, 1, 2, 3, 4),
                      limits = c("5", "4", "3", "2", "1"))

```


Save plots as images
```{r}
library(gridExtra)
library(grid)

tiff(file = "Richter.Fig2.tiff",
    width = 1200,
    height = 1200)
grid.arrange(p1, p2, ncol=, nrow = 2)
dev.off()

tiff(file = "Richter.Fig3.tiff",
    width = 1000,
    height = 800)
p3
dev.off()
```

# Checking for multicolinearity

```{r}
#calculating the median variance inflation factor across all 20 imputed datasets
col <- car::vif(fit.imp1) %>% as.data.frame()
res <- data.frame(matrix(20,14))
rownames(res) <- rownames(col)

for (i in 1:20) {
  data <- mice::complete(imp,i)
  mdl <- with(data, glm(cbind(MaxLost, MinRemain) ~ 
                Tpoints + 
                  Time + 
                  IntObs + 
                  RetroPro + 
                  PrimSec + 
                  Range + 
                  Severity + 
                  Center + 
                  Setting + 
                  Male + 
                  Age + 
                  Engage + 
                  GOS_how + 
                  HDI,
             family = binomial))
  res[,i] <- car::vif(mdl) %>% data.frame %>% select('GVIF..1..2.Df..')
}
vif.df <- apply(res,1,median) %>% data.frame
names(vif.df) <- "median_GVIFbyDF"
vif.df <- round(vif.df,2)
vif.df

#Make a pretty version of the table
vif.df %>%
  kable(escape = FALSE, row.names= TRUE) %>%
  kable_styling(bootstrap_options = c("condensed", "striped"), full_width = F)
```

# Assessing Model Fit

```{r, include=TRUE}
#I am estimating pseudoR squared for each of the 20 imputed models

res <- vector()
for (i in 1:20){
data <- mice::complete(imp, i)
mdl <- with(data, glm(cbind(MaxLost, MinRemain) ~ 
                Tpoints + 
                  Time + 
                  IntObs + 
                  RetroPro + 
                  PrimSec + 
                  Range + 
                  Severity + 
                  Center + 
                  Setting + 
                  Male + 
                  Age + 
                  Engage + 
                  GOS_how + 
                  HDI,
             family = binomial))
library(pscl)
res[i] <- pR2(mdl)[4] %>% as.vector()
}
summary(res)
```



# Complete case analysis as sensitivity analysis
```{r, include=TRUE}
complete_model <- glm(cbind(MaxLost, MinRemain) ~ 
                Tpoints + 
                  Time + 
                  IntObs + 
                  RetroPro + 
                  PrimSec + 
                  Range + 
                  Severity + 
                  Center + 
                  Setting + 
                  Male + 
                  Age + 
                  Engage + 
                  GOS_how + 
                  HDI,
             family = binomial,
             df)

# convert coefficients to odds ratios and add confidence intervals
sum <- summary(complete_model)$coefficients %>% as.data.frame()
sum$Estimate <- round(exp(sum$Estimate),2)
sum$`Pr(>|z|)` <-round(sum$`Pr(>|z|)`,2)
sum <- cbind(sum, confint(complete_model))
sum

#convert rownames to first column
sum$design <- rownames(sum)
#merge columns for confidence interval
sum$`2.5 %` <- round(exp(sum$`2.5 %`),2)
sum$`97.5 %` <- round(exp(sum$`97.5 %`),2)
sum$CI <- paste(sum$`2.5 %`, "-", sum$`97.5 %`)

sum$sig <- ifelse(sum$`2.5 %` < 1 & sum$`97.5 %` <1, "*", 
                  ifelse(sum$`2.5 %` > 1 & sum$`97.5 %` > 1, "*", ""))
#reorder and rename columns
sum <- sum %>% 
  select("Design factor" = design,
                      "Odds ratio" = Estimate,
                      "95% Confidence Interval" = CI,
        "P-value" = 'Pr(>|z|)',
                      "Significant" = sig) 

sum <- sum[-1,] # remove intercepts

myorder <-  c("Tpoints", "Time", "IntObsobservational", 
              "RetroProRetrospective", "PrimSecSecondary",  "Rangeyes", 
              "CenterSingle", "Male", "Age",  
              "HDI" ,"SeverityMild", "SeverityModerate_to_severe", 
              "SeveritySevere", "SettingAcute", "SettingSubacute",                                                  "EngageBaseline only", "EngageFollow-up only", "EngageBaseline and follow-up", 
              "GOS_howPartially in person",   "GOS_howNot in person")         
sum <- sum %>%
  mutate(`Design factor` =  factor(`Design factor`, levels = myorder)) %>%
  arrange(`Design factor`)

#Editing column Design factor
sum$`Design factor` <- gsub("Tpoints", "Total no. of follow-up timepoints",sum$`Design factor`)
sum$`Design factor` <- gsub("Time", "Study duration (months)",sum$`Design factor`)
sum$`Design factor` <- gsub("IntObsobservational", "Observational study (vs interventional)",sum$`Design factor`)
sum$`Design factor` <- gsub("RetroProProspective", "Prospective study (vs retrospective)",sum$`Design factor`)
sum$`Design factor` <- gsub("PrimSecSecondary", "GOS as secondary outcome (vs primary)",sum$`Design factor`)
sum$`Design factor` <- gsub("Rangeyes", "Use of follow-up time window (vs discrete timepoints)",sum$`Design factor`)
sum$`Design factor` <- gsub("Severity", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Setting", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Male", "Percentage of male patients",sum$`Design factor`)
sum$`Design factor` <- gsub("Age", "Mean age of study population",sum$`Design factor`)
sum$`Design factor` <- gsub("Engage", "",sum$`Design factor`)
sum$`Design factor` <- gsub("GOS_how", "",sum$`Design factor`)
sum$`Design factor` <- gsub("Severe", "Severe only",sum$`Design factor`)
sum$`Design factor` <- gsub("CenterSingle", "Single-center study (vs multi-center)",sum$`Design factor`)
sum$`Design factor` <- gsub("HDI", "Human development index of recruiting country",sum$`Design factor`)
sum$`Design factor` <- gsub("_", " ",sum$`Design factor`)


#making a pretty html version
sum %>%
  kable(escape = FALSE, row.names= FALSE) %>%
  kable_styling(bootstrap_options = c("condensed", "striped"), full_width = F) %>%
  pack_rows("Recruitment setting (compared to the hyperacute setting)", 14, 15) %>%
  pack_rows("Level of non-routine engagement (compared to no such engagement)", 16, 18)%>%
  pack_rows("Method of GOS collection (compared to collection exclusively in person)", 19, 20) %>%
  pack_rows("Injury severity (compared to using patients of mixed severity)", 11,13 )

```
```{r}
#compare complete case with imputed model
diff <- as.data.frame(matrix(ncol=4,nrow=20))
names(diff) <- c("design", "imp", "comp", "difference")
diff$design <- sum$`Design factor`
diff$imp <- sum_imp$`Odds ratio` 
diff$comp <- sum$`Odds ratio`
diff$difference <- (diff$imp - diff$comp)
diff
```

